\texttt{timeline} Documentation

### 2016-06-12 docs/documentation/documentation.tex
documentation

\section{Dependencies} \label{sec:dependencies}

@@

>>>>

\section{Dependencies}\label{sec:dependencies}

@@

\section{Modules}\label{sec:modules}

\subsection{APP}
This module simply creates the Flask object and resisters the routes for the front-end and for the API.
The Flask object must be used to start timeline using the \texttt{run} method of the app object. 
The source code is located in the \texttt{app.py} file.

\subsection{API}
The task of this module is to take requests from the front-end in form of AJAX calls and return the visualization primitives for the MetricsGraphics.js library as JSON objects.
The source code is located in the \texttt{api.py} file.

\subsubsection*{Time Series Plot: \texttt{api/time\_plot/\{time\_series\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Description:} This route create the visualization primitive for a simple time plot (i.e. a time plot of only one time series).
 It takes the identifier of the time series as part of the URL (e.g. \texttt{api/time\_plot/42}) and can take additional parameter.
 It may return a HTTP status code 404 if no time series with the given identifier exists and a HTTP status code 400 for invalid values for the optional GET parameter.
 \item[] \textbf{Additional Parameter:} All of the following parameter are optional.
 It is possible to only retrieve a slice of the time series using the \texttt{start\_date} and/or \texttt{end\_date} parameter.
 Each of this parameter must be an integer, which represents to UNIX time stamp of the start time of the slice and the end time of the slice, respectively. 
 Additional it is possible to add the graphs of the rolling mean and/or the rolling standard deviation to the plot.
 The \texttt{rolling\_mean\_window} and \texttt{rolling\_std\_window} parameter must be integer that represent the number of samples that is used to calculate the running mean and standard deviation, respectively.
\end{itemize}

\subsubsection*{Time Series Plots: \texttt{api/time\_plots}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} list of time series ids
 \item[] \textbf{Description:} 
\end{itemize}

\subsubsection*{Live Time Series Plot: \texttt{api/live\_plot/\{live\_time\_series\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} last received
 \item[] \textbf{Description:} 
\end{itemize}

\subsubsection*{ACF Plot: \texttt{api/acf\_plot/\{time\_series\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} max lag, scale
 \item[] \textbf{Description:} 
\end{itemize}

\subsubsection*{Forecasting Plot: \texttt{api/forecasting\_plot/\{forecast\_id\}}}
\begin{itemize}
 \item[] \textbf{Method:} GET 
 \item[] \textbf{Parameter:} none
 \item[] \textbf{Description:} 
\end{itemize}
